### 2021-07-08 doc/thesis/chapters/dsp.tex
update
draw own diagrams

\includepicture [1.0] [0] {Block design of a superhetorodyne receiver \cite[Fig.2.1]{PassosFábio2020AHSo}} {bd_superhet} {img/superheterodyne-receiver-block-diagram-2.png}

@@

\includepicture [0.9] [0] {Block design of a direct-conversion receiver \cite[Fig.2.3]{PassosFábio2020AHSo}.} {bd_direct_conversion} {img/direct-conversion-receiver-block-diagram.png}

@@

A block diagram, as well as the signal spectrum of the process is shown in Fig.\ref{fig:bd_down_conversion_spectrum}.

%\includepicture [0.6] [0] {Block diagram of a down-conversion \cite[Fig.4.3]{MatinMohammadA2018CSfE}.} {bd_down_conversion_spectrum} {img/bd-down-conversion-AM-dsb-sc}
\includepicture [1.0] [0] {Signal spectrum before the down-conversion.} {bd_down_conversion_spectrum} {img/down-conversion-AM}

@@

\begin{equation}
  f_{s} > 2*f_{signal}
\end{equation}

>>>>

\includepicture [1.0] [0] {Block design of a superhetorodyne receiver \cite[Fig.2.1]{PassosFábio2020AHSo}} {bd_superhet} {img/draw.io/superheterodyne-receiver-block-diagram}

@@

\includepicture [1.0] [0] {Block design of a direct-conversion receiver \cite[Fig.2.3]{PassosFábio2020AHSo}.} {bd_direct_conversion} {img/draw.io/direct-conversion-receiver-block-diagram}

@@

A block diagram, as well as the signal spectrum of the process is shown in Fig.\ref{fig:bd_down_conversion_spectrum}. In this example, the frequency of the LO is set to shift the signal from $f_m$ to baseband.

\includepicture [1.0] [0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

\begin{equation}
  f_{s} > 2 \cdot f_{signal}
\end{equation}
